---
title       : A Simple App that Predicts at Good Accuracy the Sub-Species of Iris Flowers
subtitle    : 
author      : Lam WM
job         : Student
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : prettify  # {highlight.js, prettify, highlight}
hitheme     : solarized_light      # 
widgets     : [mathjax, bootstrap, quiz, interactive]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Purpose

Predicts sub-species of Iris flowers based on:

1. Sepal Length

2. Sepal Width

3. Petal Length

4. Petal Width


--- .class #id 

## Conditions

Requires all four properties to be stated.

Does not yet have codes to catch errors for invalid input.

User should exercise caution when entering values for the four properties.

--- .class #id

## Application - Takes some time to load, please wait...

<iframe src = 'http://sardie.shinyapps.io/AssignmentOnGithub' height='600px'></iframe>


---

## Accuracy

```{r echo=FALSE}
library(caret)
library(e1071)
data(iris)
data <- iris
inTrain <- createDataPartition(y=data$Species, p=0.7, list=FALSE)
training <- data[inTrain,]
testing <- data[-inTrain,]
inTrain <- NULL
set.seed(32343)
model <- train(Species~., data=training, method="lda")
pred <- predict(model, testing)
accu <- length(pred[pred == testing$Species])/nrow(testing)
```
The accuracy based on the training set is: 
```{r echo=FALSE}
accu
```